---
title: "p8105_hw4_kma2162_p2"
author: "Kathryn Addabbo"
date: "October 26, 2017"
output: html_document
---

```{r load_packages, echo = FALSE, results = "hide"}
library(janitor)
library(lubridate)
library(dplyr)
```


Read and clean applicable data, modify pols_month data so that the column reads date and round down the days to the first of the month. 

```{r}
gdp = read.csv("./GDP.csv") %>%
  clean_names()

pols_month = read.csv("./pols-month.csv") %>%
  clean_names() %>%
  rename(date = mon) %>%
  lubridate::floor_date(date, "day")

```


The two datasets can then be merged by date. 

```{r}

pol_data = merge(gdp, pols_month, by = "date")
```


#can't rename value to gdp due to "."



Problem 1 Plot

Create a plot showing the distribution of post-natal days for each developmental landmark:

pups_data$pd_outcome <- factor(pups_data$pd_outcome, levels = c("ears", "pivot", "walk", 
                                                            "eyes"))
ggplot(pups_data, aes(x = pd_outcome, y = days)) + 
  geom_violin(aes(fill = pd_outcome), color = "black", alpha = 0.5) + 
  stat_summary(fun.y = median, geom = "point", color = "black", size = 1) +
  theme(legend.position = "bottom")